### 2012-10-26 Docs/makefiles/makefiles.tex

  This is a module that contains basic information about the build
  environment (compiler used, build machine, build directory, compiler
  flags, etc.).  This is created by the script {\tt make\_build\_info}
  in {\tt \$\{BOXLIB\_HOME\}/Tools/F\_scripts/} from {\tt
  GMaestro.mak} by passing in a number of makefile variables.  This is
  rewritten everytime the code is compiled.  The primary use of this
  module is writing out the {\tt job\_info} file in the plotfiles.

>>>>

  This is a module that contains basic information about the build
  environment (compiler used, build machine, build directory, compiler
  flags, etc.).  This is created by the script {\tt makebuildinfo.py}
  in {\tt \$\{BOXLIB\_HOME\}/Tools/F\_scripts/} from {\tt
  GMaestro.mak} by passing in a number of makefile variables.  This is
  rewritten everytime the code is compiled.  The primary use of this
  module is writing out the {\tt job\_info} file in the plotfiles.
